Instructions for \confname{} Proceedings

### 2019-05-15 papers/EMNLP2019/analysis2.tex
updated relation counts

\begin{table}
\small
\centering
\begin{tabular}{llcc}
\toprule
    &     relation & \% types & \% tok. \\
\midrule
\multirow{3}{*}{hierarchical} & meronym &  2.4 &  3.5 \\
& synonym &  3.8 &  3.8 \\
 & hypernym &  13.3 &  35.1 \\
 \midrule
 \multirow{3}{*}{less hierarchical} & holonym &  6.2 &  21.7 \\
& co-hyponym &  7.4 &  13.7 \\
 & hyponym &  8.6 &  14.7 \\
  \midrule
 \multirow{2}{*}{non-hierarchical} & word-not-covered &  15.7 &  3.8 \\
& complex relation &  73.1 &  59.0 \\

\bottomrule
\end{tabular}

>>>>

\begin{table}
\small
\centering
\begin{tabular}{lcc}
\toprule
         relation & \% types & \% token \\
\midrule
 meronym &  0.1 &  0.2 \\
 holonym &  0.1 &  0.4 \\
 synonym &  1.1 &  1.1 \\
 hyponym &  2.2 &  3.8 \\
 co-hyponym &  3.1 &  5.9 \\
 hypernym &  10.5 &  27.7 \\
 word-not-covered &  10.6 &  2.6 \\
 rel-not-covered &  72.2 &  58.3 \\
\bottomrule
\end{tabular}
